Experiments

### 2020-11-13 StateOfPractice/Methodology/Experiments.tex
added meeting notes into Experiments regarding procedure for modifiablity; edited comment in Questions to Developers
updated preamble and procedure of modifiability experiment

~\newpage
\section{Modifiability Experiments}
\pmi{add preamble here describing some of the notes below}

What can be done to measure modifiability?

Idea: measure sensible changes

Can we measure sensible changes? How?

We could gather qualitative data about the process of attempting to make sensible changes. Perceived difficulty, available documentation, prerequisite knowledge, time/effort required, tools required, errors and issues encountered and ability to overcome those issues with the available resources, is there dev support? How to interpret results?

What does a small change mean? What are likely changes - See Parnas

@@

We want to be explicit about what we want to modify.

\subsection {Procedure}
\begin{enumerate}
	\item Identify likely changes using procedure x
	\item Select from likely change list (using what criteria)
	\item Gather relevant documentation?
	\item Ask the domain expert to make the (selected) likely change(s)
	\item Have the domain expert answer a questionnaire about their attempt to make the likely change
\end{enumerate}

>>>>

~\newpage
\section{Modifiability Experiment}

This experiment is designed to gather qualitative data regarding the modifiability of each software package in a domain. The steps outlined below will result in the creation, by domain experts, of a list of likely changes for software in the domain. This list will then be used to analyze which software packages have been designed to accommodate these expected modifications.

@@

\subsection {Procedure}

\begin{enumerate}
	\item \textit{Domain Expert}: List all likely changes that a domain expert might make in a software package in the domain.
	\item Using the short list of software packages listed in the  \href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/Methodology/Methodology.pdf}{methodology document}:
	\begin{enumerate}
		\item Identify which of the above changes each package is likely designed to accommodate.
		\item Prepare a short report outlining the likely changes for software in the domain, and which changes each software package is likely designed to accommodate.
	\end{enumerate}
\end{enumerate}
